  \cvsection{Experience}
\begin{cventries}
  \cventry
    {Senior Director of Engineering, Core Services and Seattle Site Lead}
    {Splunk}
    {Seattle, WA}
    {2013 - PRESENT}
    {
      \begin{cvitems}
        \item {Engineering leader for Core Services at Splunk, managing 80 engineers across three locations.}
        \item {Site Lead for the Seattle office, drove office investment and growth from four people to over sixty today across multiple functions.}
        \item {Managed, hired and developed a team of engineers ranging in seniority from junior to principal engineers.}
        \item {Driving technical and product strategy for Splunk across multiple areas.}
        \item {Led development and architecture for several critical technical initiatives, including HTTP ingestion, Splunk's KV Store, and improvements to Splunk's manageability and scalability.}
        \item {Global engineering release lead for multiple releases of Splunk's flagship product, Splunk Enterprise.}
        \item {Initiated and drove multiple cross-organizational initiatives to improve Splunk's engineering process, such as source control, code reviews, continuous integration and interviewing.}
        \item {Regular interaction with customers for technical enablement, roadmap and support discussions.}
      \end{cvitems}
    }
  \cventry
    {Senior Software Engineer}
    {Splunk}
    {Seattle, WA}
    {2011 - 2013}
    {
      \begin{cvitems}
        \item {Founding engineer of Splunk's Seattle, the first office out of the Bay Area.}
        \item {Led technical direction and architecture for our Developer Platform initiative, including Splunk's SDKs, Tooling and Web Framework.}
        \item {Lead developer for several of our SDKs and the Splunk Web Framework.}
      \end{cvitems}
    }
  \cventry
    {Software Design Engineer II - Technical Strategy Incubation (Midori)}
    {Microsoft}
    {Redmond, WA}
    {2008 - 2011}
    {
      \begin{cvitems}
        \item {Designed and implemented a capability-based security system for low-level resources in a next- generation operating system.}
        \item {Designing and implementing synergistic scenarios between OS and hypervisor, including enlightened video and debugging services.}
        \item {Involved in design and implementation of various aspects of system, from low-level subsystems to high-level applications and services.}
      \end{cvitems} 
    }
  \cventry
    {Software Design Engineer Intern - Media Foundation/Windows Experience}
    {Microsoft}
    {Redmond, WA}
    {Jun. 2007 - Aug. 2007}
    {
      \begin{cvitems}
        \item {Developed multimedia playback scenario in Media Foundation and Windows Media Player, shipped as part of Windows 7.}
        \item {Implemented metadata solution through Media Foundation for new media format. }
      \end{cvitems}
    }
%   \cventry
%     {Research and Development Intern}
%     {Bloomberg}
%     {New York, NY}
%     {Dec. 2011 - Feb. 2012}
%     {
%       \begin{cvitems}
%         \item {Developed a dynamic administration system for a product, from specification to implementation.}
%         \item {Wrote functional documentation for legacy FORTRAN code at client request.}
%       \end{cvitems}
%     }
\end{cventries}
